Tropical Andes Taxonomic Diversity of Plants and Frugivores

### 2024-06-24 code/L2/L2_1_TropicalAndes_taxdiv.Rmd
adjust plots before combining into multi-panel plots, remove geometry from richness dataframes before saving as csv

---
title: "Tropical Andes Taxonomic Diversity of Plants and Frugivores"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "Calculating and mapping taxonomic diversity as species richness using occurrence data for plants and frugivores in the Tropical Andes Moist Lowland and Montane forests. Note: some code is adapted from https://luisdva.github.io/rstats/richness/."
#data input: "TropicalAndes_plant_occ.csv, TropicalAndes_frugivore_occ.csv"
#data output: "TropicalAndes_frugivore_richness.csv, TropicalAndes_GBIF_plant_richness.csv"
date: "2023-08-01"
output: 
  html_document:
    highlight_downlit = TRUE
    df_print: tibble
---

@@

# Multi panel plots of richness maps
## Plants
```{r}
# Add labels and remove axis labels from all plots
plantgridRichTA_5km_labeled <- plantgridRichTA_5km + ggtitle("5 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
plantgridRichTA_10km_labeled <- plantgridRichTA_10km + ggtitle("10 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
plantgridRichTA_25km_labeled <- plantgridRichTA_25km + ggtitle("25 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
plantgridRichTA_50km_labeled <- plantgridRichTA_50km + ggtitle("50 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
plantgridRichTA_75km_labeled <- plantgridRichTA_75km + ggtitle("75 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
plantgridRichTA_100km_labeled <- plantgridRichTA_100km + ggtitle("100 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
plantgridRichTA_100km_labeled
```

@@

```{r}
all_plant_richness_plots_labeled <- ggpubr::annotate_figure(all_plant_richness_plots,
                                                            left = ggpubr::text_grob("Plants", face = "bold", size = 14, 
                                                                                     rot = 90))
all_plant_richness_plots_labeled
ggsave("plant_richness_plots.png", all_plant_richness_plots_labeled, path = figure_path, width = 20, height = 5, units = "in")
```

## Frugivores
```{r}
# Add labels and remove axis labels from all plots
frugivoregridRichTA_5km_labeled <- frugivoregridRichTA_5km + ggtitle("5 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_10km_labeled <- frugivoregridRichTA_10km + ggtitle("10 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_25km_labeled <- frugivoregridRichTA_25km + ggtitle("25 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_50km_labeled <- frugivoregridRichTA_50km + ggtitle("50 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_75km_labeled <- frugivoregridRichTA_75km + ggtitle("75 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_100km_labeled <- frugivoregridRichTA_100km + ggtitle("100 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_100km_labeled
```

@@

```{r}
all_frugivore_richness_plots_labeled <- ggpubr::annotate_figure(all_frugivore_richness_plots,
                                                            left = ggpubr::text_grob("Frugivores", face = "bold", size = 14,
                                                                                     rot = 90))
all_frugivore_richness_plots_labeled
ggsave("frugivore_richness_plots.png", all_frugivore_richness_plots_labeled, path = figure_path, width = 20, height = 4, units = "in")
```

@@

ggsave("all_richness_plots.png", all_richness_plots, path = figure_path, width = 20, height = 8, units = "in")
```

# Write data to csv
```{r}
write.csv(plant_cellRichness_5km, file.path(output_path,"TropicalAndes_plantRichness_5km.csv"))
write.csv(frugivore_cellRichness_5km, file.path(output_path,"TropicalAndes_frugivoreRichness_5km.csv"))
```

```{r}
write.csv(plant_cellRichness_10km, file.path(output_path,"TropicalAndes_plantRichness_10km.csv"))
write.csv(frugivore_cellRichness_10km, file.path(output_path,"TropicalAndes_frugivoreRichness_10km.csv"))
```

```{r}
write.csv(plant_cellRichness_25km, file.path(output_path,"TropicalAndes_plantRichness_25km.csv"))
write.csv(frugivore_cellRichness_25km, file.path(output_path,"TropicalAndes_frugivoreRichness_25km.csv"))
```

```{r}
write.csv(plant_cellRichness_50km, file.path(output_path,"TropicalAndes_plantRichness_50km.csv"))
write.csv(frugivore_cellRichness_50km, file.path(output_path,"TropicalAndes_frugivoreRichness_50km.csv"))
```

```{r}
write.csv(plant_cellRichness_75km, file.path(output_path,"TropicalAndes_plantRichness_75km.csv"))
write.csv(frugivore_cellRichness_75km, file.path(output_path,"TropicalAndes_frugivoreRichness_75km.csv"))
```

```{r}
write.csv(plant_cellRichness_100km, file.path(output_path,"TropicalAndes_plantRichness_100km.csv"))
write.csv(frugivore_cellRichness_100km, file.path(output_path,"TropicalAndes_frugivoreRichness_100km.csv"))
```

>>>>

---
title: "Tropical Andes Taxonomic Diversity of Plants and Frugivores"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "Calculating and mapping taxonomic diversity as species richness using occurrence data for plants and frugivores in the Tropical Andes Moist Lowland and Montane forests. Note: some code is adapted from https://luisdva.github.io/rstats/richness/."
date: "2023-08-01"
output: 
  html_document:
    highlight_downlit = TRUE
    df_print: tibble
---

@@

# Multi panel plots of richness maps
## Plants
```{r}
# Add labels and remove axis labels from all plots
plantgridRichTA_5km_labeled <- plantgridRichTA_5km + ggtitle("5 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
plantgridRichTA_10km_labeled <- plantgridRichTA_10km + ggtitle("10 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
plantgridRichTA_25km_labeled <- plantgridRichTA_25km + ggtitle("25 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
plantgridRichTA_50km_labeled <- plantgridRichTA_50km + ggtitle("50 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
plantgridRichTA_75km_labeled <- plantgridRichTA_75km + ggtitle("75 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
plantgridRichTA_100km_labeled <- plantgridRichTA_100km + ggtitle("100 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
plantgridRichTA_100km_labeled
```

@@

```{r}
all_plant_richness_plots_labeled <- ggpubr::annotate_figure(all_plant_richness_plots,
                                                            left = ggpubr::text_grob("Plants", face = "bold", size = 20, 
                                                                                     rot = 90))
all_plant_richness_plots_labeled
ggsave("plant_richness_plots.png", all_plant_richness_plots_labeled, path = figure_path, width = 16, height = 5, units = "in")
```

## Frugivores
```{r}
# Add labels and remove axis labels from all plots
frugivoregridRichTA_5km_labeled <- frugivoregridRichTA_5km + ggtitle("5 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
frugivoregridRichTA_10km_labeled <- frugivoregridRichTA_10km + ggtitle("10 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
frugivoregridRichTA_25km_labeled <- frugivoregridRichTA_25km + ggtitle("25 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
frugivoregridRichTA_50km_labeled <- frugivoregridRichTA_50km + ggtitle("50 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
frugivoregridRichTA_75km_labeled <- frugivoregridRichTA_75km + ggtitle("75 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
frugivoregridRichTA_100km_labeled <- frugivoregridRichTA_100km + ggtitle("100 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1), legend.key.height = unit(0.5, "in"), legend.text = element_text(size = 10))
frugivoregridRichTA_100km_labeled
```

@@

```{r}
all_frugivore_richness_plots_labeled <- ggpubr::annotate_figure(all_frugivore_richness_plots,
                                                            left = ggpubr::text_grob("Frugivores", face = "bold", size = 20,
                                                                                     rot = 90))
all_frugivore_richness_plots_labeled
ggsave("frugivore_richness_plots.png", all_frugivore_richness_plots_labeled, path = figure_path, width = 16, height = 5, units = "in")
```

@@

ggsave("all_richness_plots.png", all_richness_plots, path = figure_path, width = 16, height = 10, units = "in")
```

# Write data to csv
Have to remove geometry before saving to csv
```{r}
plant_cellRichness_5km_df <- data.frame(cellid = plant_cellRichness_5km$cellid,
                                        num_species = plant_cellRichness_5km$num_species)
frugivore_cellRichness_5km_df <- data.frame(cellid = frugivore_cellRichness_5km$cellid,
                                            num_species = frugivore_cellRichness_5km$num_species)

plant_cellRichness_10km_df <- data.frame(cellid = plant_cellRichness_10km$cellid,
                                        num_species = plant_cellRichness_10km$num_species)
frugivore_cellRichness_10km_df <- data.frame(cellid = frugivore_cellRichness_10km$cellid,
                                            num_species = frugivore_cellRichness_10km$num_species)

plant_cellRichness_25km_df <- data.frame(cellid = plant_cellRichness_25km$cellid,
                                        num_species = plant_cellRichness_25km$num_species)
frugivore_cellRichness_25km_df <- data.frame(cellid = frugivore_cellRichness_25km$cellid,
                                            num_species = frugivore_cellRichness_25km$num_species)

plant_cellRichness_50km_df <- data.frame(cellid = plant_cellRichness_50km$cellid,
                                        num_species = plant_cellRichness_50km$num_species)
frugivore_cellRichness_50km_df <- data.frame(cellid = frugivore_cellRichness_50km$cellid,
                                            num_species = frugivore_cellRichness_50km$num_species)

plant_cellRichness_75km_df <- data.frame(cellid = plant_cellRichness_75km$cellid,
                                        num_species = plant_cellRichness_75km$num_species)
frugivore_cellRichness_75km_df <- data.frame(cellid = frugivore_cellRichness_75km$cellid,
                                            num_species = frugivore_cellRichness_75km$num_species)

plant_cellRichness_100km_df <- data.frame(cellid = plant_cellRichness_100km$cellid,
                                        num_species = plant_cellRichness_100km$num_species)
frugivore_cellRichness_100km_df <- data.frame(cellid = frugivore_cellRichness_100km$cellid,
                                            num_species = frugivore_cellRichness_100km$num_species)
```

```{r}
write.csv(plant_cellRichness_5km_df, file.path(output_path,"TropicalAndes_plantRichness_5km.csv"), row.names = FALSE)
write.csv(frugivore_cellRichness_5km_df, file.path(output_path,"TropicalAndes_frugivoreRichness_5km.csv"), row.names = FALSE)
```

```{r}
write.csv(plant_cellRichness_10km_df, file.path(output_path,"TropicalAndes_plantRichness_10km.csv"), row.names = FALSE)
write.csv(frugivore_cellRichness_10km_df, file.path(output_path,"TropicalAndes_frugivoreRichness_10km.csv"), row.names = FALSE)
```

```{r}
write.csv(plant_cellRichness_25km_df, file.path(output_path,"TropicalAndes_plantRichness_25km.csv"), row.names = FALSE)
write.csv(frugivore_cellRichness_25km_df, file.path(output_path,"TropicalAndes_frugivoreRichness_25km.csv"), row.names = FALSE)
```

```{r}
write.csv(plant_cellRichness_50km_df, file.path(output_path,"TropicalAndes_plantRichness_50km.csv"), row.names = FALSE)
write.csv(frugivore_cellRichness_50km_df, file.path(output_path,"TropicalAndes_frugivoreRichness_50km.csv"), row.names = FALSE)
```

```{r}
write.csv(plant_cellRichness_75km_df, file.path(output_path,"TropicalAndes_plantRichness_75km.csv"), row.names = FALSE)
write.csv(frugivore_cellRichness_75km_df, file.path(output_path,"TropicalAndes_frugivoreRichness_75km.csv"), row.names = FALSE)
```

```{r}
write.csv(plant_cellRichness_100km_df, file.path(output_path,"TropicalAndes_plantRichness_100km.csv"), row.names = FALSE)
write.csv(frugivore_cellRichness_100km_df, file.path(output_path,"TropicalAndes_frugivoreRichness_100km.csv"), row.names = FALSE)
```
